
\documentclass[A4,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{tikz}
\input{glyphtounicode}
\usepackage{palatino}


% Adjust margins
\addtolength{\oddsidemargin}{-1cm}
\addtolength{\evensidemargin}{-1cm}
\addtolength{\textwidth}{2cm}
\addtolength{\topmargin}{-1cm}
\addtolength{\textheight}{2cm}



\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0cm}

% Sections formatting
\titleformat{\section}{
\vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that .pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-----CUSTOM COMMANDS FOR FORMATTING SECTIONS----------------------------------

\newcommand{\ProjectEntry}[2]{%
  \item
  \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
    \textbf{#1} & #2 \\
  \end{tabular*}\vspace{-5pt}
}

\newcommand{\CVItem}[1]{
\item\small{
  {#1 \vspace{-2pt}}
}
}

\newcommand{\CVSubheading}[4]{
\vspace{-2pt}\item
  \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
    \textbf{#1} & #2 \\
    \small#3 & \small #4 \\
  \end{tabular*}\vspace{-7pt}
}

\newcommand{\CVSubSubheading}[2]{
  \item
  \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
    \text{\small#1} & \text{\small #2} \\
  \end{tabular*}\vspace{-7pt}
}

\newcommand{\CVSubItem}[1]{\CVItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\CVSubHeadingListStart}{\begin{itemize}[leftmargin=0.5cm, label={}]}
% \newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]} % Uncomment for US
\newcommand{\CVSubHeadingListEnd}{\end{itemize}}
\newcommand{\CVItemListStart}{\begin{itemize}}
\newcommand{\CVItemListEnd}{\end{itemize}\vspace{-5pt}}

%------------------------------------------------------------------------------
% CV STARTS HERE  %
%------------------------------------------------------------------------------
\begin{document}

%-----HEADING------------------------------------------------------------------
\begin{comment}
In Europe it is common to include a picture of ones self in the CV. Select
which heading appropriate for the document you are creating.
\end{comment}


   %Without picture
\begin{center}
    \textbf{\Huge \scshape Hello Helloxx \\ \vspace{1pt} %\scshape sets small capital letters, remove if desired
    \small +91-6386419509 $|$ 
    \href{mailto:2228090@kiit.ac.in}{\underline{2228090@kiit.ac.in}} $|$ \href{https://hello.com}{\underline{hello.com}}  $|$ \\ 
    \href{https://lkdn.om/adiv1313}{\underline{lkdn.om/adiv1313}}  $|$
    % you should adjust you linked in profile name to be professional and recognizable
    \href{https://gthub.com/adi13v}{\underline{gthub.com/adi13v}}
\end{center}
  




\begin{comment}
This CV was written for specifically for positions I was applying for in
academia, and then modified to be a template.

A standard CV is about two pages long where as a resume in the US is one page.
sections can be added and removed here with this in mind. In my experience, 
education, and applicable work experience and skills are the most import things
to include on a resume. For a CV the Europass CV suggests the categories: Work
Experience, Education and Training, Language Skills, Digital Skills,
Communication and Interpersonal Skills, Conferences and Seminars, Creative Works
Driver's License, Hobbies and Interests, Honors and Awards, Management and
Leadership Skills, Networks and Memberships, Organizational Skills, Projects,
Publications, Recommendations, Social and Political Activities, Volunteering.

Your goal is to convey a who, what , when, where, why for every item you share. 
The who is obviously you, but I believe the rest should be done in that order.
For example below. An employer cares most about the degree held and typically 
less about the institution or where it is located (This is still good 
information though). Whatever order you choose be consistent throughout.
\end{comment}

%-----EDUCATION----------------------------------------------------------------
\section{Education}
\CVSubHeadingListStart
\CVSubheading
    {{Bachelor of Science $|$ \emph{\small{Computer Science}}}} {Sep. 2016 -- May 2020}
    {Stanford University $|$ Stanford, California}{CGPA: 3.8}
  \CVSubheading
    {{Bachelor of Arts $|$ \emph{\small{Mathematics}}}} {Sep. 2014 -- May 2016}
    {University of California, Berkeley $|$ Berkeley, California}{CGPA: 3.7}
  
\CVSubHeadingListEnd

%-----WORK EXPERIENCE----------------------------------------------------------
\section{Work Experience}
  \CVSubHeadingListStart
  \CVSubheading
    {Senior Software Engineer}{Jun. 2022 -- Present}
    {Google}{Mountain View, California}
    \CVItemListStart
      \CVItem{Led development of \textbf{scalable} microservices architecture handling 1M+ daily requests}\CVItem{Implemented CI/CD pipeline reducing deployment time by 40\%}\CVItem{Mentored junior developers and conducted code reviews for team of 5 engineers}
    \CVItemListEnd
      \CVSubheading
    {Software Engineer}{Jun. 2020 -- May 2022}
    {Microsoft}{Redmond, Washington}
    \CVItemListStart
      \CVItem{Developed and maintained Azure cloud services with 99.99\% uptime}\CVItem{Optimized database queries reducing response time by 30\%}\CVItem{Collaborated with cross-functional teams to deliver features on schedule}
    \CVItemListEnd
      
  \CVSubHeadingListEnd
  
%-----PROJECTS AND RESEARCH----------------------------------------------------


\section{Projects}
\CVSubHeadingListStart
\CVSubheading
    {AI-Powered Resume Builder}{Jan. 2023 - Present}
    {\href{https://github.com/username/resume-builder}{\color{blue}Github Link}}{}
    \CVItemListStart
      \CVItem{Real-time LaTeX PDF generation with custom templates}\CVItem{AI-powered content suggestions and grammar checking}\CVItem{Responsive design with dark/light mode support}\CVItem{Local storage for draft saving and auto-recovery}
    \CVItemListEnd
\CVSubheading
    {Distributed Task Scheduler}{Jul. 2022 - Dec. 2022}
    {\href{https://github.com/username/task-scheduler}{\color{blue}Github Link}}{}
    \CVItemListStart
      \CVItem{Implemented distributed consensus using Raft algorithm}\CVItem{Achieved 99.9\% task execution reliability}\CVItem{Scaled to handle 100K+ concurrent tasks}\CVItem{Added monitoring and alerting system}
    \CVItemListEnd
\CVSubHeadingListEnd


%-----HONORS AND AWARDS--------------------------------------------------------

\section{Honors and Achievments}
\CVSubHeadingListStart
  \CVSubheading
    {Dean's List}{May 2023}
    {Recognition for academic excellence in Computer Science program}{\href{https://example.com/certificate}{\color{blue}Certificate}}
    \CVSubheading
    {Best Project Award}{Dec. 2022}
    {Awarded for outstanding performance in the annual project competition}{\href{https://example.com/profile}{\color{blue}Profile Link}}
    
\CVSubHeadingListEnd


%-----CLUBS AND SOCIETIES--------------------------------------------------------

  \section{Clubs And Societies}
  \CVSubHeadingListStart
  \CVSubheading
    {Web Development DD}{Jan. 2023 - Jan. 2024}
    {KIIT MLSA} {}
    \CVSubheading
    {Public Speaking Mentor}{Aug. 2022 - Aug. 2023}
    {KIIT MUN Society} {}
    
  \CVSubHeadingListEnd
  

%-----Certifications-------------------------------------------------------------------

  \section{Certifications}
  \CVSubHeadingListStart
  \item \small
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      
        \textbf{AWS Cloud Practitioner} & 
        \href{https://example.com/certificate1}{\color{blue}Certificate Link} \\
        
        \textbf{Google Cloud Professional Data Engineer} & 
        \href{https://example.com/certificate2}{\color{blue}Certificate Link} \\
        
    \end{tabular*}
    \end{itemize}
  

%-----SKILLS-------------------------------------------------------------------

  \section{Skills}
  \begin{itemize}[leftmargin=0.5cm, label={}]
    \small{\item{
      \textbf{Languages}{: Python, JavaScript, TypeScript, Java, C++} \\ \textbf{Frameworks}{: React, Node.js, Express, Django, Spring Boot} \\ \textbf{Developer Tools}{: Git, Docker, Kubernetes, AWS, Azure, CI/CD} \\ \textbf{Databases}{: MongoDB, PostgreSQL, Redis, MySQL} \\ \textbf{Soft Skills}{: Leadership, Team Collaboration, Problem Solving, Communication}
      }}
      \end{itemize}
  
  
%------------------------------------------------------------------------------
\end{document}